%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Deepak}{Kumar}{ \urlstyle{same}\href{https://deepak-kumar.netlify.app}{deepak-kumar.netlify.app }| \href{https://www.linkedin.com/in/deepak-kumar-bb1810115/}{deepak@linkedin } \\
\href{mailto:kumar.de@northeastern.edu}{kumar.de@northeastern.edu}| 857.891.0357 |
{01 Copenger Street, Boston, MA 02120}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Northeastern University}
\descript{MS in Computer Science}
\location{Sep 2019 - Dec 2021 | Boston, MA}
Khoury College of Computer Sciences \\
\location{ GPA: 4.0 / 4.0}
\sectionsep

\subsection{Visvesvaraya Technological University}
\descript{BE in Information Science}
\location{Aug 2012 - May 2016 | Hassan, India}
Malnad College of Engineering \\
\location{ GPA: 8.52 / 10}
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/itachi1994}{\bf @itachi1994} \\
LinkedIn://  \href{https://www.linkedin.com/in/deepak-kumar-bb1810115/}{\bf deepak-kumar} \\
Website://  \href{https://deepak-kumar.netlify.app/}{\bf deepakkumar} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Programming Design Paradigm \\
Database Management System \\
Web Development \\
Algorithms \\
Foundation of Software Engineering \\
Information Retrieval \\
\sectionsep

\subsection{Undergraduate}
Object-Oriented Programming \\
Operating Systems \\
Data Structures \\
User Interface \\
Web Development \\
Unix Tools and Scripting \\
Cryptography \\
Computer Networks\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Programming Languages:}
Java \textbullet{} JavaScript ES6
 \textbullet{}  TypeScript\\ \textbullet{} SAP ABAP\\ 
\location{Framework:}
Node.js \textbullet{} React.js \textbullet{} React Native \textbullet{} Spring Boot \textbullet{} Maven \textbullet{} Express.js\\
\location{Databases:}
MySQL \textbullet{} MongoDB \textbullet{} DynamoDB\\
\location{Cloud and Services:}
AWS \textbullet{} Azure \textbullet{} OCI \textbullet{}
Jira \textbullet{} Jenkins \textbullet{} Git \textbullet{} SVN \textbullet{} BitBucket \textbullet{} GitLab \textbullet{} Docker\\ \textbullet{} Firebase \textbullet{} Heroku \textbullet{} Splunk\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Northeastern University}
\descript{| Teaching Assistant }
\location{Sep 2020 - Present | Boston, MA}

\sectionsep

\runsubsection{Slalom Build}
\descript{| Software Engineering Intern }
\location{June 2020 – Aug 2020 | Boston, MA}
\textbf{Stagen Leadership App | \emph{React Native, AWS, Node.js, TypeScript, Bit Bucket, JIRA} }
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Led Cloud, DevOps, and Security effort in the team of 12. Provisioned AWS infrastructure using infrastructure as code, built Bit Bucket pipelines, and integrated front-end with App Center.
\item Collaborated on Stagen Mobile App - the mobile user interface for Stagen leadership platform.
\item Full-stack developer - Wrote and reviewed code for TypeScript, Node.js, and React Native. 
\end{tightemize}
\sectionsep

\runsubsection{Brillio}
\descript{| Software Engineer }
\location{Aug 2016 – Aug 2019 | Bengaluru, India}
\textbf{Server To Serverless | \emph{Node.js, AWS, Python, HTML, JQuery, CSS, SVN, JIRA} }
\begin{tightemize}
\item Implemented application by migrating Python server-based code to serverless code using Node.js and AWS, which increased the response time of application by 20 \%.
\item Created and deployed RESTful API’s using API Gateway. Used CloudFormation to create and manage AWS resources.
\end{tightemize}
\sectionsep
\textbf{Notification Mechanism  | \emph{Node.js, AWS, GiT, JIRA, Splunk } }
\begin{tightemize}
\item Developed a mechanism to send notifications on change of an attribute of a property listing, which helped stakeholders to make more informed decisions, resulting in a 15 \% increase in returning customer base.
\item Achieved 100 \% unit test coverage by following test-driven development using Chai Mocha. Followed the agile software development process and contributed to sprint planning and retrospective.
\end{tightemize}
\sectionsep

\textbf{OptiGST | \emph{SAP ABAP, Java } }
\begin{tightemize}

\item Collaborated on OptiGST - an ERP solution in response to new taxation regime introduced in India in 2016. 
\item OptiGST is used daily by more than 20 big organizations for GST compliance.


\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Academic and Personal Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Academic \& Personal Projects}
% \runsubsection{Cornell Robot Learning Lab}
% \descript{| Researcher}
\textbf{Image Processing Application | \emph{Java, Git}} \\
% Worked with \textbf{\href{http://www.cs.cornell.edu/~ashesh/}{Ashesh Jain}} and \textbf{\href{http://www.cs.cornell.edu/~asaxena/}{Prof Ashutosh Saxena}} to create \textbf{PlanIt}, a tool which  learns from large scale user preference feedback to plan robot trajectories in human environments.  
Built an Image processing application to apply six filters on an image such as greyscale, sepia, mosaic, dithering, blur, and sharpen using MVC architecture and design patterns. 
\sectionsep


% \runsubsection{Cornell Phonetics Lab}
% \descript{| Head Undergraduate Researcher}
\textbf{BookBar e-Commerce Website | \emph {Node.js, MongoDB, React.js, Redux, Heroku}}\\
% Led the development of \textbf{QuickTongue}, the first ever breakthrough tongue-controlled game with \textbf{\href{http://conf.ling.cornell.edu/~tilsen/}{Prof Sam Tilsen}} to aid in Linguistics research. 
Collaborated on building a full stack web app that manages different user profiles, scopes, and log in. The application provides a platform for buyers and sellers to buy and sell books.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certification} 
2020	      \location{AWS Certified Developer Associate}
2020	     \location{AWS Certified Solution Architect Associate}
2020	     \location{Oracle Cloud Infrastructure Foundation Associate}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Publications} 
% \renewcommand\refname{\vskip -1.5em} % Couldn't get this working from the .cls file
% \bibliographystyle{abbrv}
% \bibliography{publications}
% \nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
